---
author: Funke Alliyu and Lauryn Pavlik
date: April 30th, 2019
title: "Stat 380 Final Project"
output: html_notebook
---


```{r}
# Clean up environment
rm(list = ls())

# Load packages
library(tidyverse)
library(readr)
library(utils)
library(dplyr)
library(tidyverse)
library(mdsr)
library(mosaic)
library(stringr)
library(tidytext)
library(janeaustenr)
library(wordcloud)


# Add data 
raw_fed_data <- 
  read_csv("dif source join.csv")
NCANDS <- 
  read_csv("Findings from NCANDS - Data Tables (updated with FY 2015).csv")

# User-defined functions
## circle
circle <- function(center = c(0, 0), npoints = 100) {
    r = 1
    tt = seq(0, 2 * pi, length = npoints)
    xx = center[1] + r * cos(tt)
    yy = center[1] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}

```

# Data Table One

```{r}
# View fed data
head(raw_fed_data)

```
This data set was found on data.gov.

# Data Table Two

```{r}
# View NCANDS data
head(NCANDS)

```
This data is from https://www.acf.hhs.gov/cb/resource/child-maltreatment-2014-data-tables.

## Cleaning Federal Data

### Making a totals table 

```{r}
# Make totals seperate table from fed_data
fed_totals <-
  raw_fed_data %>%
  filter(`Measure 2` == "Total")

```

```{r}
# Clean fed_totals
fed_totals <- 
  fed_totals %>%
  rename(Measure_2 = 'Measure 2',  Measure_1 = 'Measure 1') %>%
  spread(key = Format, value = Value) 

```

```{r}
# Remove columns
fed_totals <- 
  fed_totals %>%
  select(-'X7', -'Measure_1', -'Measure_2')

```

```{r}
# Rename remaining variables
fed_totals <- 
  fed_totals %>%
  rename(Num_fatalities = 'Number', Rate_per_100000 = 'Rate per 100,000 Children')

```

Here we have created a table containing the total number of child abuse fatalities from each state and the child fatality rate per 100,000 children. It is important to note that data for Maine and Massachusetts were not provided, but data for Puerto Rico and the District of Columbia were provided making the total number of cases 50. 

### Cleaning original table

```{r}
# Rename and spread; remove unimportant columns for analysis
fed_data <- 
  raw_fed_data %>%
  rename(Measure_2 = 'Measure 2',  Measure_1 = 'Measure 1') %>%
  spread(key = Measure_2, value = Value) %>%
  spread(key = Format, value = Total) %>%
  select(-`Rate per 100,000 Children`, -`X7`) %>%  
  mutate(id = row_number())

```

```{r}
# Remove even rows with all NAs
for (i in 1){
    if (TRUE) {
        fed_data <- fed_data[fed_data$id %% 2 == 1, ]
       }
}

```

```{r}
# Finish cleaning
fed_data[is.na(fed_data)] = 0     # Set useful N/As to zero

fed_data <- 
  fed_data %>%
  rename(Num_agencyfile = `Reported in the Agency File`, 
         Num_childfile = `Reported in the Child File`, 
         Total = Number) %>%
  select(-`Measure_1`, -`id`)
  
```

```{r}
# Add rates
fed_data <-
  full_join(fed_data, fed_totals) %>%    # Join to add rates column into new table
  select(-Total)

fed_data <- 
  fed_data %>%
  mutate(State_num = row_number()) # Add index to cases for easier graph visualization
  
```
Here, we have made a table of 50 cases (same issues with states as fed_totals table) and included the variables pertaining to the number of child abuse cases that went into differing files, total number of fatalities, and the rate of child abuse fatalities per 100,0000 children. Again, even rows were removed due to a containment of excessive N/As. The remaining N/As were set to zero because they were in the files column. With observation, one can see that if you add the number of Num_agencyfile and Num_childfile for that row, that sum is the Num_fatalities column. We also have assigned a number to label each case because it will make graph visualizations in the future easier to understand. 

## Cleaning NCANDS Data By Breaking Down Tables

```{r}
# Rename to make spreading easier
NCANDS <-
  NCANDS %>%
  rename(Characteristic = `Characteristic Label`)

```
In the following chunks of code, we will be filtering the different tables out of the enormous NCANDS data to clean all the tables and make them tidy. Each table has a title describing the contents of it. Each of these tables all revolve around the topic of child abuse.


### Make fatality_sub_type

```{r}
# Table for child abuse fatalities by their submission type
fatality_sub_type <-
  NCANDS %>%
  filter(Table == "Child Fatalities by Submission Type") %>% # Filter to receive desired table
  select(- "Measure") %>%
  spread(key = Characteristic, value = Value) %>%
  spread(key = Format, value = Total) %>%
  select(-Rate) %>%
   mutate(id = row_number())

```

```{r}
# Remove even rows with all NAs
for (i in 1){
    if (TRUE) {
        fatality_sub_type <- 
          fatality_sub_type[fatality_sub_type$id %% 2 == 1, ]
       }
}

```

```{r}
# Finish cleaning
fatality_sub_type[is.na(fatality_sub_type)] = 0

fatality_sub_type <- 
  fatality_sub_type %>%
  rename(Num_agencyfile = `Reported in the Agency File`,
         Num_childfile = `Reported in the Child File`) %>%
  select(-`id`)

```

### Make fatality_trend

```{r} 
# Table to show the trends of child abuse fatalities
fatality_trend <-
  NCANDS %>%
  filter(Table == "Child Fatalities, Trend") %>%   # Filter to receive desired table
  spread(key = Measure, value = Value) %>%
  spread(key = Year, value = `Child fatalities`) %>%
  select(- Characteristic, - Format)

```

### Make victim_age

```{r}
# Table to show the victims' ages 
victim_age <-
  NCANDS %>%
  filter(Table == "Child Victims by Age") %>%   # Filter to receive desired table
  spread(key = Characteristic, value = Value) %>%
  mutate(id = row_number())

```

```{r}
# Remove even rows with all NAs
for (i in 1){
    if (TRUE) {
        victim_age <- victim_age[victim_age$id %% 2 == 1, ]
       }
}

```


```{r}
# Remove rows that do not have a match in other tables 
victim_age <- 
  victim_age[-c(20, 28, 41), ]

victim_age[[24]] <- NULL

victim_age <- 
  victim_age %>%
  select(- Measure, - `id`) %>%
  rename(Age_under1 = `Age <1`, Age_1 = `Age 1`, Age_10 = `Age 10`, Age_11 = `Age 11`, 
         Age_12 = `Age 12`, Age_13 = `Age 13`, Age_14 = `Age 14`, Age_15 = `Age 15`, 
         Age_16 = `Age 16`, Age_17 = `Age 17`, Age_2 = `Age 2`, Age_3 = `Age 3`, 
         Age_4 = `Age 4`, Age_5 = `Age 5`, Age_6 = `Age 6`, Age_7 = `Age 7`, 
         Age_8 = `Age 8`, Age_9 = `Age 9`)


```

### Make case_type 

```{r}
# Table that shows the different case types and results
case_type <-
  NCANDS %>%
  filter(Table == "Children by Disposition") %>%    # Filter to receive desired table
  spread(key = Measure, value = Value) %>%
  select(- `Nonvictims (duplicate count) by disposition`, -Format) %>%
  spread(key = Characteristic, value = `Victims (duplicate count) by disposition`) %>%
  select(- `Alternative Response`, - `Closed With No Finding`, - `Indicated`, 
         - `Intentionally False`, - `No Alleged Maltreatment`, - `Other`, - `Unknown`, 
         - `Unsubstantiated`)
case_type <- 
  case_type[-c(20, 28, 41), ]

```

### Make investigation

```{r}
# Table to show how many cases received an investigation
investigation <-
  NCANDS %>%
  filter(Table == "Children Who Received an Investigation or Alternative Response, Trend") %>%
  spread(key = Measure, value = Value) %>%
  select(- `Children (unique count) who received an investigation or alternative response, rate per 1,000 children`) %>%
  spread(key = Year, 
         value = `Children (unique count) who received an investigation or alternative response`)%>%
  select(- Characteristic, - Format) %>%
  mutate(id = row_number())

```

```{r}
# Remove even rows with NAs
for (i in 1){
    if (TRUE) {
        investigation <- investigation[investigation$id %% 2 == 1, ]
       }
}

investigation <-
  investigation[-c(20, 28, 41), ]

```

### Make mal_type 

```{r}
# Table to show how many children suffered a specific type of abuse 
mal_type <-
  NCANDS %>%
  filter(Table == "Maltreatment Types of Victims") %>%   # Filter to receive desired table
  spread(key = Measure, value = Value) %>%
  spread(key = Characteristic, value = `Victims (unique count) by maltreatment type`)

mal_type <- 
  mal_type[-c(20, 28, 41), ]

mal_type[is.na(mal_type)] = 0  # Change N/As to 0 to represent no data being recorded for that year

mal_type <- 
  mal_type %>%
  rename(Med_neglect = `Medical Neglect`, Physical_abuse = `Physical Abuse`, 
         Psych_abuse = `Psychological Maltreatment`, Sexual_abuse = `Sexual Abuse`) 


```

### Make perpetrator_tally

```{r}
# Table to show the abuser's relationship to the victim
perpetrator_tally <-
  NCANDS %>%
  filter(Table == "Perpetrators by Relationship to their Victims") %>% # Filter to receive desired table
  spread(key = Measure, value = Value) %>%
  spread(key = Characteristic,
         value = `Perpetrators (unique count) by relationship to their victims`) %>%
  select(- Format)

perpetrator_tally[is.na(perpetrator_tally)] = 0

perpetrator_tally <- 
  perpetrator_tally %>%
  rename(Daycare_provider = `Child Daycare Provider`, Foster_parent = `Foster Parent`,
         Friend_neighbor = `Friend and Neighbor`, 
         Group_home = `Group Home and Residential Facility Staff`,
         Guardian = `Legal Guardian`, Multiple = `Multiple Relationships`,
         Other_professional = `Other Professional`, 
         Other_relative = `Other Relative`, Unmarried_partner = `Unmarried Partner of Parent`)

```

### Make perpetrator_total

```{r}
# Table to show the amounts of perpetrators known in each year for each case
perpetrator_total <-
  NCANDS %>%
  filter(Table == "Perpetrators, Trend") %>% # Filter to receive desired table
  spread(key = Measure, value = Value) %>%
  select(- Format, - Characteristic) %>%
  spread(key = Year, value = `Perpetrators (unique count)`) 

perpetrator_total[is.na(perpetrator_total)] = 0

perpetrator_total <- 
  perpetrator_total[-c(19, 27), ]

```

### Make referral_type

```{r}
# Table to show values for types of referrals
referral_type <-
  NCANDS %>%
  filter(Table == "Screened-In and Screened-Out Referrals") %>% # Filter to receive desired table
  spread(key = Measure, value = Value) %>%
  select(- `Referrals, percent of total`, - `Referrals, rate per 1,000 children`,
         - Format) %>%
  mutate(id = row_number())

```


```{r}
# Remove even rows with all NAs
for (i in 1){
    if (TRUE) {
        referral_type <- referral_type[referral_type$id %% 2 == 1, ]
       }
}

```

```{r}
# Table that shows the type of referral dealing with the child abuse cases
referral_type<- 
  referral_type %>%
  spread(key = Characteristic, value = Referrals) %>%
  select(- Total)

referral_type[is.na(referral_type)] = 0

referral_type <-
  referral_type %>%
  rename(Screen_in = `Screened-In Referrals (Reports)`, Screen_out = `Screened-Out Referrals`)

referral_type$Total <- referral_type$Screen_in + referral_type$Screen_out # Add a column that shows the total of both types of referrals

```

# Join Tables From Different Sources

```{r}
# Make one big table
All_data <-
  fed_data %>%
  full_join(by = "State", case_type) %>%
  full_join(by = "State", fatality_sub_type) %>%
  full_join(by = "State", fatality_trend) %>%
  full_join(by = "State", investigation) %>%
  full_join(by = "State", mal_type) %>%
  full_join(by = "State", perpetrator_tally) %>%
  full_join(by = "State", perpetrator_total) %>%
  full_join(by = "State", referral_type) %>%
  full_join(by = "State", victim_age) 

``` 

```{r}
# Rename variables to keep
All_data <- 
  All_data %>%
  rename(Num_agencyfile2014 = Num_agencyfile.x, Num_childfile2014 = Num_childfile.x, 
         Num_fatalities2014 = Num_fatalities, Rate2014 = Rate_per_100000,
         Substantiated_case = Substantiated, Num_agencyfile2015 = Num_agencyfile.y,
         Num_childfile2015 = Num_childfile.y, Num_fatalities2015 = Number, 
         Num_fatalities2011 = `2011.x`, Num_fatalities2012 = `2012.x`, 
         Num_fatalities2013 = `2013.x`, Invest2011 = `2011.y`, Invest2012 = `2012.y`,
         Invest2013 = `2013.y`, Invest2014 = `2014.y`, Invest2015 = `2015.y`,
         Other_abuse = Other.x, Unknown_abuse = Unknown.x, Other_perp = Other.y,
         Unknown_perp = Unknown.y, Perp2011 = `2011`, Perp2012 = `2012`,
         Perp2013 = `2013`, Perp2014 = `2014`, Perp2015 = `2015`, Total_screened = Total) %>%
  select(- `Year.x`, - `Year.y`, - `Table.x`, - `Year.x.x`, - `Table.y`, - `Table.x.x`,
         - `2014.x`, - `2015.x`, - `Table.y.y`, - `Year.y.y`, - `Table.x.x.x`, - `Format.x`,
         - `Year.x.x.x`, - `Table.y.y.y`, - `Table.x.x.x.x`, - `Year.y.y.y`, - `Table.y.y.y.y`,
         - `Year`, - `Table`, - `Format.y`, - `Rate2014`)

All_data[is.na(All_data)] = 0

All_data <- 
  All_data[-c(38, 52, 53), ]
  
```
Here we have joined all the relevant tables together to make one big data table for analysis. 


# Data Visualization 

## Graph 1 

```{r}
# Layered graph
Graph_1 <- 
  ggplot() +
  geom_line(data = All_data, aes(State_num, Num_fatalities2014, color = "Num_fatalities2014")) +
  geom_point(data = fed_data, aes(State_num, Rate_per_100000, color = "Rate_per_100000")) +
  xlab("State ID") +
  ylab("Number of Fatalities") +
  ggtitle("2014 Fatality Data By State")

plot(Graph_1)
  
```
Graph number 1 compares the number of child abuse fatalities in 2014 to the rate of fatalities per 100,000 children in 2014. With observation, one can see that there are sharp spikes in the number of fatalities around certain state ids. These spikes occur around 5, 10, 21, 31, and 43, which correspond to California, Florida, Michigan, New York, and Texas. An interesting observation is that Vermont (number 45) only had 1 fatality that year. The rates at the bottom of the graph strongly follow the trend of direction with the number of fatalities as common sense would suggest. 

## Graph 2

```{r}
# Multiple variables graph 
Graph_2 <- 
  All_data %>%
  ggplot() +
  geom_point(aes(x = State_num, y = Num_fatalities2011, color = "Num_fatalities2011")) +
  geom_point(aes(x = State_num, y = Num_fatalities2012, color = "Num_fatalities2012")) +
  geom_point(aes(x = State_num, y = Num_fatalities2013, color = "Num_fatalities2013")) +
  geom_point(aes(x = State_num, y = Num_fatalities2014, color = "Num_fatalities2014")) +
  geom_point(aes(x = State_num, y = Num_fatalities2015, color = "Num_fatalities2015")) + 
  ggtitle("Number of Child Abuse Fatalities From 2011 To 2015") +
  xlab("Number Corresponding To State From Table") +
  ylab("Number of Child Abuse Fatalities")

plot(Graph_2)

```
Graph number 2 compares child fatalities across 5 years, versus 1 year like graph 1. The color of dots that seem to be the highest fatality year are army green, purple, and green. These correspond to 2012, 2013, and 2015. Two state ids seem to stick out with higher fatalities, being 1 and 43, which are Alabama and Texas.

## Graph 3 

```{r}
# Multiple variables graph
Graph_3 <- 
  All_data %>%
  ggplot() +
  geom_line(aes(State_num, Invest2011, color = "Invest2011")) +
  geom_line(aes(State_num, Invest2012, color = "Invest2012")) +
  geom_line(aes(State_num, Invest2013, color = "Invest2013")) +
  geom_line(aes(State_num, Invest2014, color = "Invest2014")) +
  geom_line(aes(State_num, Invest2015, color = "Invest2015")) + 
  ggtitle("Number of Investigations From 2011 To 2015") +
  xlab("Number Corresponding To State From Table") +
  ylab("Number of Investigations")

plot(Graph_3)

```
Graph 3 shows the number of investigations in child abuse cases over 5 years. An interesting observation is that the same states that spiked in graph 1 - California, Florida, Michigan, New York, and Texas - also spike in this graph. 2015 seems to have the highest number of investigations most consistently. 

## Graph 4

```{r}
# Multiple variables graph
Graph_4 <- 
  All_data %>%
  ggplot() +
  geom_area(aes(State_num, Med_neglect, color = "Med_neglect")) +
  geom_area(aes(State_num, Neglect, color = "Neglect")) +
  geom_area(aes(State_num, Other_abuse, color = "Other_abuse")) +
  geom_area(aes(State_num, Physical_abuse, color = "Physical_abuse")) +
  geom_area(aes(State_num, Psych_abuse, color = "Psych_abuse")) + 
  geom_area(aes(State_num, Sexual_abuse, color = "Sexual_abuse")) +
  geom_area(aes(State_num, Unknown_abuse, color = "Unknown_abuse")) +
  ggtitle("Types of Abuse") +
  xlab("Number Corresponding To State From Table") +
  ylab("Number of Victims That Suffered")

plot(Graph_4)


```
Graph 4 shows the number of victims suffering from each type of abuse over the states. The 'other' variable seems to contain the highest trend. Physical abuse and psychological abuse are the next two most common types of abuse. There seems to be little unknown abuse. Sexual abuse is still present, but not as prominent.

# Article on Child Abuse 

https://www.nspcc.org.uk/what-we-do/childrens-stories-about-abuse/ 

This website provides different childs' abuse stories. We have gathered a collection of 5 abuse stories compiled into a word document

```{r}
# Input text for analysis 
Stories <- 
  read.delim("Child abuse stories.txt", header = FALSE, fill = TRUE)

# Note it is being stored as a data frame of length 1
str(Stories)

length(Stories)

```  

```{r}
# str_replace returns a character vector
Stories  <-
  Stories$V1 %>%
  str_replace_all("(\x92)+", "'") %>% 
  str_replace_all("(\x93)+", "'") 

str(Stories)
length(Stories)

```


```{r}
# Subset Margaret's story
margaret_story <-
  data.frame(Stories[c(2:14)]) %>%
  mutate(text = Stories.c.2.14..) %>%
  select(- Stories.c.2.14..)

head(margaret_story)

```

```{r}
# unnest_tokens expects a character vector
text <-
  margaret_story$text %>%
  as.character()

# Create a data frame
text_df <-
  data_frame(line = 1:13, text = text)

text_df

margaret_story_analysis <-
  text_df %>%
  unnest_tokens(word, text)

```
Throughout the past few code chunks, we have cleaned up the text document that contains stories about child abuse and chose one story in particular- Margaret. Her story relays to sexual abuse and how she worries her children will react to their abusive father later in life. In the next section of code, we will see which words are most prominent throughout the story and if they can provide any more insight into her story. 


#### Token Frequency

```{r}
# See word counts
margaret_story_analysis %>%
  count(word, sort = TRUE)

```

```{r}
# Load stop word list
data("stop_words")
head(stop_words)
tail(stop_words)

```

```{r}
# View word count table
margaret_story_analysis <-
  margaret_story_analysis %>%
  filter(!(word %in% stop_words$word))

margaret_story_analysis %>%
  count(word, sort = TRUE)

```

```{r}
# Create wordcloud
margaret_story_analysis %>%
  filter(!(word %in% stop_words$word)) %>%
  count(word) %>%
  with(., wordcloud(word, n, max.words = 45))



```

```{r}
data("sentiments")
head(sentiments, 10)
tail(sentiments, 10)
```

```{r}
get_sentiments("nrc") %>%
  group_by(sentiment) %>%
  summarise(N= n()) %>%
  arrange(desc(N))
```

#### Sentiment Analysis on Margaret's Story

```{r}

nrc_fear <-
  get_sentiments("nrc") %>%
  filter(sentiment == "fear")

margaret_story_analysis %>%
  inner_join(nrc_fear) %>%
  count(word, sort = TRUE)

```




### Unsupervised Learning

Maltreatment Type by State

 We want to compare states on:
  + Medical Neglect
  + Neglect
  + Physical Abuse
  + Pyschological Abuse
  + Sexual Abuse
  + Other
  + Unknown

```{r}
# Add rownames so that State is not treated as a variable
rownames(mal_type) <-
  mal_type$State

mal_analysis <-
  mal_type %>%
  select(- Table, - Format, - Year, -State)

head(mal_analysis)

```

```{r}
# Standardize vriables
mal_pca <-
  mal_analysis %>%
  prcomp(scale = TRUE)

# Result is a list
str(mal_pca)
```

```{r}
# First two principal components

(-1) * mal_pca$rotation[, 1:2] %>%
  round(2)

```
```{r}

head(mal_pca$x)

```

### Principal Components Plot

```{r}
# Plot first two principal components
mal_pca$x %>%
  as.data.frame() %>%  # ggplot uses data frames
  rownames_to_column() %>%
  ggplot(aes(x = -PC1, y = -PC2)) +
  geom_text(aes(label = rowname), size = 3)+
  xlab("Best Vector from PCA (approx. Unknown)") +
  ylab("2nd Best Vector from PCA (approx. Medical Neglect)") +
  ggtitle("2-Dimensional Representation of Maltreatment by State")

```

### Circle Correlations Plot

```{r}
circle <- function(center = c(0, 0), npoints = 100) {
    r = 1
    tt = seq(0, 2 * pi, length = npoints)
    xx = center[1] + r * cos(tt)
    yy = center[1] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}
corcir = circle(c(0, 0), npoints = 100)

# create data frame with correlations between variables and PCs
correlations = as.data.frame(cor(mal_analysis, mal_pca$x))


# data frame with arrows coordinates
arrows = data.frame(x1 = c(0, 0, 0, 0, 0, 0, 0),
                    y1 = c(0, 0, 0, 0, 0, 0, 0),
                    x2 = correlations$PC1,
                    y2 = correlations$PC2)

# geom_path will do open circles
ggplot() + 
  geom_path(data = corcir, aes(x = x, y = y),
            colour = "gray65") + 
    geom_segment(data = arrows,
                 aes(x = x1, y = y1, xend = x2, yend = y2),
                 colour = "gray65") + 
    geom_text(data = correlations, aes(x = PC1, y = PC2,
            label = rownames(correlations))) + 
    geom_hline(yintercept = 0, colour = "gray65") +
  geom_vline(xintercept = 0, 
             colour = "gray65") + 
  xlim(-1.1, 1.1) +
  ylim(-1.1, 1.1) + 
  labs(x = "pc1 aixs", 
       y = "pc2 axis") + ggtitle("Circle of correlations")

```

### Scree Plot (Maltreatment Type Data)

```{r}

mal_pve <- 
  data.frame(sd = mal_pca$sdev) %>%
  rownames_to_column() %>%
  mutate(rowname = parse_number(rowname), 
         totalVar = sum(mal_pca$sdev^2), 
         pve = 100 * sd^2 / totalVar, 
         cusum = cumsum(pve))

# scree plot
mal_pve %>%
  ggplot(aes(x = rowname, y = pve)) + 
  geom_line(type = 3) + 
  xlab("Principal Component") + 
  ylab("Proportion of Variance Explained") + 
  ggtitle("Scree Plot of Principal Components for Maltreatment Type Data") 

```

The plot above shows that ~ 4 components explains around 89% variance in the data set. In order words, using PCA we have reduced 7 predictors to 4 without compromising much on explained variance. This is the power of PCA. Let's confirm by plotting a cumulative variance plot. This will give us a clear picture of number of components.

```{r}
# cumulative PVE plot
mal_pve %>%
  ggplot(aes(x = rowname, y = cusum)) + 
  geom_line(type = 3) + 
  xlab("Principal Component") + 
  ylab("Proportion of Variance Explained") + 
  ggtitle("Cumulative Proportion of Variance Explained for Maltreatment Type Data")

```

This plot shows that 4 components results in variance close to ~ 90%. Therefore, in this case, we’ll select number of components as 4 [PC1 to PC4] and proceed to the modeling stage. For modeling, we’ll use these 4 components as predictor variables and follow the normal procedures.

## Data Analysis

### Statistical Modeling

Research Question: Which years are associated with the total number of perpretators for the year in the DMV?

#### Data Preparation

```{r}
# set RNG seed for reproducible results
set.seed(622) 

# partition the data
n <- nrow(perpetrator_total)

test_idx <- 
  sample.int(n, size = round(0.25 * n))  # select row numbers for the test set

train <-
  perpetrator_total[-test_idx, ]  # exclude the test set cases

nrow(train)

```

```{r}

test <- perpetrator_total[test_idx, ]    # test set cases only

nrow(test)

```









